---
title: "Influences of STEM policy part 1"
output: html_notebook
---
First, I will read the data I need and ignore the rest of the columns I don't need.

```{r}
setwd("F:/sly/ads")
library(data.table)
library(ggplot2)
library(plyr)
library(choroplethr)
library(choroplethrMaps)
col_need <- c("ADJINC","ST","CIT","SCH","SCHL","OD1P","FOD1P","WAOB","SCIENGP","SCIENGRLP","POBP")
stem_major<-c(1103,1104,1105,1106,1301,1401,2100,2101,2102,2105,2106,2107,
              2400,2401,2402,2403,2404,2407,2408,2409,2410,2411,2412,2413,
              2414,2415,2416,2417,2418,2419,2499,2500,2501,2502,2503,2504,
              2599,3600,3601,3602,3603,3604,3605,3606,3607,3608,3609,3611,
              3699,3700,3701,3702,3801,4002,4005,4006,5000,5001,5002,5003,
              5004,5005,5006,5007,5008,5102,5206,5901,6105,6202,6212)

pus11a <- fread("ss11pusa.csv",select = col_need)
pus11b <- fread("ss11pusb.csv",select = col_need)
pus12a <- fread("ss12pusa.csv",select = col_need)
pus12b <- fread("ss12pusb.csv",select = col_need)
pus13a <- fread("ss13pusa.csv",select = col_need)
pus13b <- fread("ss13pusb.csv",select = col_need)
pus14a <- fread("ss14pusa.csv",select = col_need)
pus14b <- fread("ss14pusb.csv",select = col_need)

pus11a <- as.data.frame(pus11a)
pus11b <- as.data.frame(pus11b)

pus12a <- as.data.frame(pus12a)
pus12b <- as.data.frame(pus12b)

pus13a <- as.data.frame(pus13a)
pus13b <- as.data.frame(pus13b)

pus14a <- as.data.frame(pus14a)
pus14b <- as.data.frame(pus14b)

```

I create data for each year from 2011 to 2014 and each year has stem and none-stem data.

```{r}
###### 11
pus11a <- pus11a[which(is.na(pus11a$FOD1P)==FALSE),]
pus11a_stem <- pus11a[pus11a$FOD1P %in% stem_major,]
pus11a_non_stem <- pus11a[!(pus11a$FOD1P %in% stem_major),]

pus11b <- pus11b[which(is.na(pus11b$FOD1P)==FALSE),]
pus11b_stem <- pus11b[pus11b$FOD1P %in% stem_major,]
pus11b_non_stem <- pus11b[!(pus11b$FOD1P %in% stem_major),]

data_11_stem <- rbind(pus11a_stem,pus11b_stem)
data_11_non_stem <- rbind(pus11a_non_stem,pus11b_non_stem)

####### 12 
pus12a <- pus12a[which(is.na(pus12a$FOD1P)==FALSE),]
pus12a_stem <- pus12a[pus12a$FOD1P %in% stem_major,]
pus12a_non_stem <- pus12a[!(pus12a$FOD1P %in% stem_major),]

pus12b <- pus12b[which(is.na(pus12b$FOD1P)==FALSE),]
pus12b_stem <- pus12b[pus12b$FOD1P %in% stem_major,]
pus12b_non_stem <- pus12b[!(pus12b$FOD1P %in% stem_major),]

data_12_stem <- rbind(pus12a_stem,pus12b_stem)
data_12_non_stem <- rbind(pus12a_non_stem,pus12b_non_stem)


####### 13
pus13a <- pus13a[which(is.na(pus13a$FOD1P)==FALSE),]
pus13a_stem <- pus13a[pus13a$FOD1P %in% stem_major,]
pus13a_non_stem <- pus13a[!(pus13a$FOD1P %in% stem_major),]

pus13b <- pus13b[which(is.na(pus13b$FOD1P)==FALSE),]
pus13b_stem <- pus13b[pus13b$FOD1P %in% stem_major,]
pus13b_non_stem <- pus13b[!(pus13b$FOD1P %in% stem_major),]

data_13_stem <- rbind(pus13a_stem,pus13b_stem)
data_13_non_stem <- rbind(pus13a_non_stem,pus13b_non_stem)

####### 14

pus14a <- pus14a[which(is.na(pus14a$FOD1P)==FALSE),]
pus14a_stem <- pus14a[pus14a$FOD1P %in% stem_major,]
pus14a_non_stem <- pus14a[!(pus14a$FOD1P %in% stem_major),]

pus14b <- pus14b[which(is.na(pus14b$FOD1P)==FALSE),]
pus14b_stem <- pus14b[pus14b$FOD1P %in% stem_major,]
pus14b_non_stem <- pus14b[!(pus14b$FOD1P %in% stem_major),]

data_14_stem <- rbind(pus14a_stem,pus14b_stem)
data_14_non_stem <- rbind(pus14a_non_stem,pus14b_non_stem)
```

Up to now, we have create all the data we need.
Then we will see the stem and none stem people change in the four years.
To begin with, I created the data that we need to draw plots.

```{r}
year11_stem_num <- nrow(data_11_stem)
year12_stem_num <- nrow(data_12_stem)
year13_stem_num <- nrow(data_13_stem)
year14_stem_num <- nrow(data_14_stem)

year11_none_stem_num <- nrow(data_11_non_stem)
year12_none_stem_num <- nrow(data_12_non_stem)
year13_none_stem_num <- nrow(data_13_non_stem)
year14_none_stem_num <- nrow(data_14_non_stem)

draw_data <- c(year11_stem_num,year12_stem_num,year13_stem_num,year14_stem_num)
draw_data <- cbind(c(2011,2012,2013,2014),draw_data)
colnames(draw_data) <- c("year","people")
draw_data <- as.data.frame(draw_data)

draw_data_1 <- c(year11_none_stem_num,year12_none_stem_num,year13_none_stem_num,year14_none_stem_num)
draw_data_1 <- cbind(c(2011,2012,2013,2014),draw_data_1)
colnames(draw_data_1) <- c("year","people")
draw_data_1 <- as.data.frame(draw_data_1)
```

We plot the change of STEM people from 2011 to 2014.

```{r}
ggplot(data=draw_data,aes(x=year,y=people))+
  geom_line(colour="steelblue1",size=2)+
  geom_point(size=2)+
  ggtitle("STEM People")
```

From the plot we can see that the STEM people were steady growing.
Next, we plot the none-STEM trend.
```{r}
ggplot(data=draw_data_1,aes(x=year,y=people))+
  geom_line(colour="steelblue1",size=2)+
  geom_point(size=2)+
  ggtitle("None-STEM People")
```

We can see that growing trend of STEM and none-STEM are similar.
Then we will see how the STEM people ratio change during the four years.

```{r}
stem_ratio_11 <- year11_stem_num/(year11_stem_num+year11_none_stem_num)
stem_ratio_12 <- year11_stem_num/(year12_stem_num+year12_none_stem_num)
stem_ratio_13 <- year11_stem_num/(year13_stem_num+year13_none_stem_num)
stem_ratio_14 <- year11_stem_num/(year14_stem_num+year14_none_stem_num)

draw_data_2 <- c(stem_ratio_11,stem_ratio_12,stem_ratio_13,stem_ratio_14)
draw_data_2 <- cbind(c(2011,2012,2013,2014),draw_data_2)
colnames(draw_data_2) <- c("year","people")
draw_data_2 <- as.data.frame(draw_data_2)

ggplot(data=draw_data_2,aes(x=year,y=people))+
  geom_line(colour="steelblue1",size=2)+
  geom_point(size=2)+
  ggtitle("STEM People Ratio")

```

From the plot we can see that the ratio of STEM people have droped slightly, from about 20 percent to 18.5 percent.

