---
title: "Influences of STEM policy part 2"
output: html_notebook
---

### By Qing Yin and Yueqi Zhang

Before we start to analyze data, we should clean the data. The cleaning and preprocessing process for this part has been done by Yueqi Zhang, so the data sets that I analyze below are assumed to be clean.

First, I should set the work directory and load the data sets that I need into R workspace.
```{r}
setwd("G:/Columbia/STAT GR5243/project01")
pus11<-read.csv("fndata2011.csv")
pus12<-read.csv("fndata2012.csv")
pus13<-read.csv("fndata2013.csv")
pus14<-read.csv("fndata2014.csv")
```

Then, I need to separate each data set into two parts according to citizenship status.
```{r}
pus11cit<-pus11[pus11$CIT==1,]
pus11ncit<-pus11[pus11$CIT==0,]
pus12cit<-pus12[pus12$CIT==1,]
pus12ncit<-pus12[pus12$CIT==0,]
pus13cit<-pus13[pus13$CIT==1,]
pus13ncit<-pus13[pus13$CIT==0,]
pus14cit<-pus14[pus14$CIT==1,]
pus14ncit<-pus14[pus14$CIT==0,]
```

Now, for the convenience of further study, we first have a look at a small part of our data in a table.
```{r}
library(DT)
datatable(head(pus11cit,50),options=list(scrollX=T,pageLength=10))
```

In order to get top majors in both stem fields and non-stem fields, I need to obtain the frequency of each major in each data set and sort majors by frequencies for each data set.
```{r}
topmajors13cit<-as.data.frame(sort(table(pus13cit$FOD1P),decreasing=T))
topmajors13ncit<-as.data.frame(sort(table(pus13ncit$FOD1P),decreasing=T))
topmajors14cit<-as.data.frame(sort(table(pus14cit$FOD1P),decreasing=T))
topmajors14ncit<-as.data.frame(sort(table(pus14ncit$FOD1P),decreasing=T))
colnames(topmajors13cit)<-"frequency"
colnames(topmajors13ncit)<-"frequency"
colnames(topmajors14cit)<-"frequency"
colnames(topmajors14ncit)<-"frequency"
```

Now, I generate stem/non-stem vectors for major vectors. 
```{r}
majorstemv13cit<-vector()
majorstemv13ncit<-vector()
majorstemv14cit<-vector()
majorstemv14ncit<-vector()
for(i in 1:nrow(topmajors13cit)){
  majorstemv13cit[i]<-(pus13cit[pus13cit$FOD1P==as.numeric(rownames(topmajors13cit)[i]),which(colnames(pus13cit)=="STEM")])[1]
}
for(i in 1:nrow(topmajors13ncit)){
  majorstemv13ncit[i]<-(pus13ncit[pus13ncit$FOD1P==as.numeric(rownames(topmajors13ncit)[i]),which(colnames(pus13ncit)=="STEM")])[1]
}
for(i in 1:nrow(topmajors14cit)){
  majorstemv14cit[i]<-(pus14cit[pus14cit$FOD1P==as.numeric(rownames(topmajors14cit)[i]),which(colnames(pus14cit)=="STEM")])[1]
}
for(i in 1:nrow(topmajors14ncit)){
  majorstemv14ncit[i]<-(pus14ncit[pus14ncit$FOD1P==as.numeric(rownames(topmajors14ncit)[i]),which(colnames(pus14ncit)=="STEM")])[1]
}
```

We need to generate major vs stem matrix now.
```{r}
library(dplyr)
ms13cit<-topmajors13cit%>%mutate(major=rownames(topmajors13cit))
ms13cit<-ms13cit%>%mutate(stem=majorstemv13cit)
ms13cit<-ms13cit%>%mutate(proportion=frequency/sum(frequency))

ms13ncit<-topmajors13ncit%>%mutate(major=rownames(topmajors13ncit))
ms13ncit<-ms13ncit%>%mutate(stem=majorstemv13ncit)
ms13ncit<-ms13ncit%>%mutate(proportion=frequency/sum(frequency))

ms14cit<-topmajors14cit%>%mutate(major=rownames(topmajors14cit))
ms14cit<-ms14cit%>%mutate(stem=majorstemv14cit)
ms14cit<-ms14cit%>%mutate(proportion=frequency/sum(frequency))

ms14ncit<-topmajors14ncit%>%mutate(major=rownames(topmajors14ncit))
ms14ncit<-ms14ncit%>%mutate(stem=majorstemv14ncit)
ms14ncit<-ms14ncit%>%mutate(proportion=frequency/sum(frequency))
```

Now, I will preprocess data for Sankey plot.
```{r}
ms13citallns<-ms13cit%>%filter(stem==0)
ms13citalls<-ms13cit%>%filter(stem==1)
ms13cittopns<-rbind(ms13citallns[1:20,],c(sum(ms13citallns[-(1:20),1]),"other",0,sum(ms13citallns[-(1:20),4])))
ms13cittops<-rbind(ms13citalls[1:20,],c(sum(ms13citalls[-(1:20),1]),"other",1,sum(ms13citalls[-(1:20),4])))
ms13cittop<-rbind(ms13cittops,ms13cittopns)

ms13ncitallns<-ms13ncit%>%filter(stem==0)
ms13ncitalls<-ms13ncit%>%filter(stem==1)
ms13ncittopns<-rbind(ms13ncitallns[1:20,],c(sum(ms13ncitallns[-(1:20),1]),"other",0,sum(ms13ncitallns[-(1:20),4])))
ms13ncittops<-rbind(ms13ncitalls[1:20,],c(sum(ms13ncitalls[-(1:20),1]),"other",1,sum(ms13ncitalls[-(1:20),4])))
ms13ncittop<-rbind(ms13ncittops,ms13ncittopns)

ms14citallns<-ms14cit%>%filter(stem==0)
ms14citalls<-ms14cit%>%filter(stem==1)
ms14cittopns<-rbind(ms14citallns[1:20,],c(sum(ms14citallns[-(1:20),1]),"other",0,sum(ms14citallns[-(1:20),4])))
ms14cittops<-rbind(ms14citalls[1:20,],c(sum(ms14citalls[-(1:20),1]),"other",1,sum(ms14citalls[-(1:20),4])))
ms14cittop<-rbind(ms14cittops,ms14cittopns)

ms14ncitallns<-ms14ncit%>%filter(stem==0)
ms14ncitalls<-ms14ncit%>%filter(stem==1)
ms14ncittopns<-rbind(ms14ncitallns[1:20,],c(sum(ms14ncitallns[-(1:20),1]),"other",0,sum(ms14ncitallns[-(1:20),4])))
ms14ncittops<-rbind(ms14ncitalls[1:20,],c(sum(ms14ncitalls[-(1:20),1]),"other",1,sum(ms14ncitalls[-(1:20),4])))
ms14ncittop<-rbind(ms14ncittops,ms14ncittopns)
```

The following function is used to transfer major codes into major names
```{r}
codename<-function(code){
  name<-"other"
  if(code==1100) name<-"general agriculture"
  if(code==1101) name<-"agriculture production and management"
  if(code==1102) name<-"agricultural economics"
  if(code==1103) name<-"animal sciences"
  if(code==1104) name<-"food science"
  if(code==1105) name<-"plant science and agronomy"
  if(code==1106) name<-"soil science"
  if(code==1199) name<-"miscellaneous agriculture"
  if(code==1301) name<-"environmental science"
  if(code==1302) name<-"forestry"
  if(code==1303) name<-"natural resources management"
  if(code==1401) name<-"architecture"
  if(code==1501) name<-"area ethnic and civilization"
  if(code==1901) name<-"communications"
  if(code==1902) name<-"journalism"
  if(code==1903) name<-"mass media"
  if(code==1904) name<-"advertising and public relations"
  if(code==2001) name<-"communication technologies"
  if(code==2100) name<-"computer and information systems"
  if(code==2101) name<-"computer programming and data processing"
  if(code==2102) name<-"computer science"
  if(code==2105) name<-"information sciences"
  if(code==2106) name<-"computer administration management and security"
  if(code==2107) name<-"computer networking and telecommunications"
  if(code==2201) name<-"cosmetology services and culinary arts"
  if(code==2300) name<-"general education"
  if(code==2301) name<-"educational administration and supervision"
  if(code==2303) name<-"school student counseling"
  if(code==2304) name<-"elementary education"
  if(code==2305) name<-"mathematics teacher education"
  if(code==2306) name<-"physical and health education teaching"
  if(code==2307) name<-"early childhood education"
  if(code==2308) name<-"science and computer teacher education"
  if(code==2309) name<-"secondary teacher education"
  if(code==2310) name<-"special needs education"
  if(code==2311) name<-"social science or history teacher education"
  if(code==2312) name<-"teacher education: multiple levels"
  if(code==2313) name<-"language and drama education"
  if(code==2314) name<-"art and music education"
  if(code==2399) name<-"miscellaneous education"
  if(code==2400) name<-"general engineering"
  if(code==2401) name<-"aerospace engineering"
  if(code==2402) name<-"biological engineering"
  if(code==2403) name<-"architectural engineering"
  if(code==2404) name<-"biomedical engineering"
  if(code==2405) name<-"chemical engineering"
  if(code==2406) name<-"civil engineering"
  if(code==2407) name<-"computer engineering"
  if(code==2408) name<-"electrical engineering"
  if(code==2409) name<-"engineering mechanics physics and science"
  if(code==2410) name<-"environmental engineering"
  if(code==2411) name<-"geological and geophysical engineering"
  if(code==2412) name<-"industrial and manufacturing engineering"
  if(code==2413) name<-"materials engneering and materials science"
  if(code==2414) name<-"mechanical engineering"
  if(code==2415) name<-"metallurgical engineering"
  if(code==2416) name<-"mining and mineral engineering"
  if(code==2417) name<-"naval architecture and marine engineering"
  if(code==2418) name<-"nuclear engineering"
  if(code==2419) name<-"petroleum engineering"
  if(code==2499) name<-"miscellaneous engineering"
  if(code==2500) name<-"engineering technologies"
  if(code==2501) name<-"engineering and industrial management"
  if(code==2502) name<-"electrical engineering technology"
  if(code==2503) name<-"industrial production technologies"
  if(code==2504) name<-"mechanical engineering related technologies"
  if(code==2599) name<-"miscellaneous engineering technologies"
  if(code==2601) name<-"linguistics and comparative language and literature"
  if(code==2602) name<-"french german latin and other common foreign language studies"
  if(code==2603) name<-"other foreign languages"
  if(code==2901) name<-"family and consumer sciences"
  if(code==3201) name<-"court reporting"
  if(code==3202) name<-"pre-law and legal studies"
  if(code==3301) name<-"english language and literature"
  if(code==3302) name<-"composition and rhetoric"
  if(code==3401) name<-"liberal arts"
  if(code==3402) name<-"humanities"
  if(code==3501) name<-"library science"
  if(code==3600) name<-"biology"
  if(code==3601) name<-"biochemical sciences"
  if(code==3602) name<-"botany"
  if(code==3603) name<-"molecular biology"
  if(code==3604) name<-"ecology"
  if(code==3605) name<-"genetics"
  if(code==3606) name<-"microbiology"
  if(code==3607) name<-"pharmacology"
  if(code==3608) name<-"physiology"
  if(code==3609) name<-"zoology"
  if(code==3611) name<-"neuroscience"
  if(code==3699) name<-"miscellaneous biology"
  if(code==3700) name<-"mathematics"
  if(code==3701) name<-"applied mathematics"
  if(code==3702) name<-"statistics and decision science"
  if(code==3801) name<-"military technologies"
  if(code==4000) name<-"multi/interdisciplinary studies"
  if(code==4001) name<-"intercultural and international studies"
  if(code==4002) name<-"nutrition sciences"
  if(code==4005) name<-"mathematics and computer science"
  if(code==4006) name<-"cognitive science and biopsychology"
  if(code==4007) name<-"interdisciplinary social sciences"
  if(code==4101) name<-"physical fitness parks recreation and leisure"
  if(code==4801) name<-"philosophy and religious studies"
  if(code==4901) name<-"theology and religious vocations"
  if(code==5000) name<-"physical sciences"
  if(code==5001) name<-"astronomy and astrophysics"
  if(code==5002) name<-"atmospheric sciences and meteorology"
  if(code==5003) name<-"chemistry"
  if(code==5004) name<-"geology and earth science"
  if(code==5005) name<-"geosciences"
  if(code==5006) name<-"oceanography"
  if(code==5007) name<-"physics"
  if(code==5008) name<-"material science"
  if(code==5098) name<-"multi-disciplinary or general science"
  if(code==5102) name<-"nuclear, industrial radiology, and biological technologies"
  if(code==5200) name<-"psychology"
  if(code==5201) name<-"educational psychology"
  if(code==5202) name<-"clinical psychology"
  if(code==5203) name<-"counseling psychology"
  if(code==5205) name<-"indsutrial and organizational psychology"
  if(code==5206) name<-"social psychology"
  if(code==5299) name<-"miscellaneous psychology"
  if(code==5301) name<-"criminal justice and fire protection"
  if(code==5401) name<-"public administration"
  if(code==5402) name<-"public policy"
  if(code==5403) name<-"human services and community organization"
  if(code==5404) name<-"social work"
  if(code==5500) name<-"general social sciences"
  if(code==5501) name<-"economics"
  if(code==5502) name<-"anthropology and archeology"
  if(code==5503) name<-"criminology"
  if(code==5504) name<-"geography"
  if(code==5505) name<-"internatinal relations"
  if(code==5506) name<-"political science and government"
  if(code==5507) name<-"sociology"
  if(code==5599) name<-"miscellaneous social sciences"
  if(code==5601) name<-"construction services"
  if(code==5701) name<-"electrical, mechanical and precision technologies and production"
  if(code==5901) name<-"transportation sciences and technologies"
  if(code==6000) name<-"fine arts"
  if(code==6001) name<-"drama and theater arts"
  if(code==6002) name<-"music"
  if(code==6003) name<-"visual and performing arts"
  if(code==6004) name<-"commercial arts and graphic design"
  if(code==6005) name<-"film video and photographic arts"
  if(code==6006) name<-"art history and criticism"
  if(code==6007) name<-"studio arts"
  if(code==6099) name<-"miscellaneous fine arts"
  if(code==6100) name<-"general medical and health services"
  if(code==6102) name<-"communication disorders sciences and services"
  if(code==6103) name<-"health and medical administrative services"
  if(code==6104) name<-"medical assisting services"
  if(code==6105) name<-"medical technologies technicians"
  if(code==6106) name<-"health and medical preparatory programs"
  if(code==6107) name<-"nursing"
  if(code==6108) name<-"pharmacy pharmaceutical sciences and administration"
  if(code==6109) name<-"treatment therapy professions"
  if(code==6110) name<-"community and public health"
  if(code==6199) name<-"miscellaneous health medical professions"
  if(code==6200) name<-"general business"
  if(code==6201) name<-"accounting"
  if(code==6202) name<-"actuarial science"
  if(code==6203) name<-"business management and administration"
  if(code==6204) name<-"operations logistics and e-commerce"
  if(code==6205) name<-"business economics"
  if(code==6206) name<-"marketing and marketing research"
  if(code==6207) name<-"finance"
  if(code==6209) name<-"human resources and personnel management"
  if(code==6210) name<-"international business"
  if(code==6211) name<-"hospitality management"
  if(code==6212) name<-"management information systems and statistics"
  if(code==6299) name<-"miscellaneous business and medical administration"
  if(code==6402) name<-"history"
  if(code==6403) name<-"united states history"
  return(name)
}
```

Then I will transfer major codes to major names and stem code to stem/non-stem.
```{r}
for(i in 1:nrow(ms13cittop)){
  ms13cittop[i,which(colnames(ms13cittop)=="major")]<-codename(ms13cittop$major[i])
}
for(i in 1:nrow(ms13ncittop)){
  ms13ncittop[i,which(colnames(ms13ncittop)=="major")]<-codename(ms13ncittop$major[i])
}
for(i in 1:nrow(ms14cittop)){
  ms14cittop[i,which(colnames(ms14cittop)=="major")]<-codename(ms14cittop$major[i])
}
for(i in 1:nrow(ms14ncittop)){
  ms14ncittop[i,which(colnames(ms14ncittop)=="major")]<-codename(ms14ncittop$major[i])
}
ms13cittop[ms13cittop$stem==1,which(colnames(ms13cittop)=="stem")]<-"stem"
ms13cittop[ms13cittop$stem==0,which(colnames(ms13cittop)=="stem")]<-"non-stem"
ms13ncittop[ms13ncittop$stem==1,which(colnames(ms13ncittop)=="stem")]<-"stem"
ms13ncittop[ms13ncittop$stem==0,which(colnames(ms13ncittop)=="stem")]<-"non-stem"
ms14cittop[ms14cittop$stem==1,which(colnames(ms14cittop)=="stem")]<-"stem"
ms14cittop[ms14cittop$stem==0,which(colnames(ms14cittop)=="stem")]<-"non-stem"
ms14ncittop[ms14ncittop$stem==1,which(colnames(ms14ncittop)=="stem")]<-"stem"
ms14ncittop[ms14ncittop$stem==0,which(colnames(ms14ncittop)=="stem")]<-"non-stem"
```
ms13cittop,ms13ncittop,ms14cittop,ms14ncittop will be used later.

Now, I need to do stem vs occupation type.
```{r}
stemwork13cit<-pus13cit%>%filter(STEM==1)
stemwork13ncit<-pus13ncit%>%filter(STEM==1)
stemwork14cit<-pus14cit%>%filter(STEM==1)
stemwork14ncit<-pus14ncit%>%filter(STEM==1)
nstemwork13cit<-pus13cit%>%filter(STEM==0)
nstemwork13ncit<-pus13ncit%>%filter(STEM==0)
nstemwork14cit<-pus14cit%>%filter(STEM==0)
nstemwork14ncit<-pus14ncit%>%filter(STEM==0)
topstemwork13cit<-as.data.frame(sort(table(stemwork13cit$OCCP.TYPE),decreasing=T))
topstemwork13ncit<-as.data.frame(sort(table(stemwork13ncit$OCCP.TYPE),decreasing=T))
topstemwork14cit<-as.data.frame(sort(table(stemwork14cit$OCCP.TYPE),decreasing=T))
topstemwork14ncit<-as.data.frame(sort(table(stemwork14ncit$OCCP.TYPE),decreasing=T))
topnstemwork13cit<-as.data.frame(sort(table(nstemwork13cit$OCCP.TYPE),decreasing=T))
topnstemwork13ncit<-as.data.frame(sort(table(nstemwork13ncit$OCCP.TYPE),decreasing=T))
topnstemwork14cit<-as.data.frame(sort(table(nstemwork14cit$OCCP.TYPE),decreasing=T))
topnstemwork14ncit<-as.data.frame(sort(table(nstemwork14ncit$OCCP.TYPE),decreasing=T))
topstemwork13cit<-cbind(topstemwork13cit,c("stem"))
topstemwork13ncit<-cbind(topstemwork13ncit,c("stem"))
topstemwork14cit<-cbind(topstemwork14cit,c("stem"))
topstemwork14ncit<-cbind(topstemwork14ncit,c("stem"))
topnstemwork13cit<-cbind(topnstemwork13cit,c("non-stem"))
topnstemwork13ncit<-cbind(topnstemwork13ncit,c("non-stem"))
topnstemwork14cit<-cbind(topnstemwork14cit,c("non-stem"))
topnstemwork14ncit<-cbind(topnstemwork14ncit,c("non-stem"))
colnames(topstemwork13cit)<-c("frequency","stem")
colnames(topstemwork13ncit)<-c("frequency","stem")
colnames(topstemwork14cit)<-c("frequency","stem")
colnames(topstemwork14ncit)<-c("frequency","stem")
colnames(topnstemwork13cit)<-c("frequency","stem")
colnames(topnstemwork13ncit)<-c("frequency","stem")
colnames(topnstemwork14cit)<-c("frequency","stem")
colnames(topnstemwork14ncit)<-c("frequency","stem")
topstemwork13cit<-topstemwork13cit%>%mutate(work=rownames(topstemwork13cit))
topstemwork13ncit<-topstemwork13ncit%>%mutate(work=rownames(topstemwork13ncit))
topstemwork14cit<-topstemwork14cit%>%mutate(work=rownames(topstemwork14cit))
topstemwork14ncit<-topstemwork14ncit%>%mutate(work=rownames(topstemwork14ncit))
topnstemwork13cit<-topnstemwork13cit%>%mutate(work=rownames(topnstemwork13cit))
topnstemwork13ncit<-topnstemwork13ncit%>%mutate(work=rownames(topnstemwork13ncit))
topnstemwork14cit<-topnstemwork14cit%>%mutate(work=rownames(topnstemwork14cit))
topnstemwork14ncit<-topnstemwork14ncit%>%mutate(work=rownames(topnstemwork14ncit))
topwork13cit<-rbind(topstemwork13cit,topnstemwork13cit)
topwork13ncit<-rbind(topstemwork13ncit,topnstemwork13ncit)
topwork14cit<-rbind(topstemwork14cit,topnstemwork14cit)
topwork14ncit<-rbind(topstemwork14ncit,topnstemwork14ncit)
topwork13cit[topwork13cit$work=="0",which(colnames(topwork13cit)=="work")]<-"NONE"
topwork13ncit[topwork13ncit$work=="0",which(colnames(topwork13ncit)=="work")]<-"NONE"
topwork14cit[topwork14cit$work=="0",which(colnames(topwork14cit)=="work")]<-"NONE"
topwork14ncit[topwork14ncit$work=="0",which(colnames(topwork14ncit)=="work")]<-"NONE"
topwork13cit<-topwork13cit%>%mutate(proportion=frequency/sum(frequency))
topwork13ncit<-topwork13ncit%>%mutate(proportion=frequency/sum(frequency))
topwork14cit<-topwork14cit%>%mutate(proportion=frequency/sum(frequency))
topwork14ncit<-topwork14ncit%>%mutate(proportion=frequency/sum(frequency))
```
topwork13cit, topwork13ncit, topwork14cit,topwork14ncit will be used.

Now, I am ready for Sankey plot.
```{r}
msw13cit1<-ms13cittop[,2:4]
colnames(msw13cit1)<-c("origin","visit","weight")
msw13cit2<-topwork13cit[,2:4]
colnames(msw13cit2)<-c("origin","visit","weight")
msw13cit<-rbind(msw13cit1,msw13cit2)
msw13cit[,1]<-as.factor(msw13cit[,1])
msw13cit[,2]<-as.factor(msw13cit[,2])
msw13cit[,3]<-as.numeric(msw13cit[,3])

msw13ncit1<-ms13ncittop[,2:4]
colnames(msw13ncit1)<-c("origin","visit","weight")
msw13ncit2<-topwork13ncit[,2:4]
colnames(msw13ncit2)<-c("origin","visit","weight")
msw13ncit<-rbind(msw13ncit1,msw13ncit2)
msw13ncit[,1]<-as.factor(msw13ncit[,1])
msw13ncit[,2]<-as.factor(msw13ncit[,2])
msw13ncit[,3]<-as.numeric(msw13ncit[,3])


msw14cit1<-ms14cittop[,2:4]
colnames(msw14cit1)<-c("origin","visit","weight")
msw14cit2<-topwork14cit[,2:4]
colnames(msw14cit2)<-c("origin","visit","weight")
msw14cit<-rbind(msw14cit1,msw14cit2)
msw14cit[,1]<-as.factor(msw14cit[,1])
msw14cit[,2]<-as.factor(msw14cit[,2])
msw14cit[,3]<-as.numeric(msw14cit[,3])


msw14ncit1<-ms14ncittop[,2:4]
colnames(msw14ncit1)<-c("origin","visit","weight")
msw14ncit2<-topwork14ncit[,2:4]
colnames(msw14ncit2)<-c("origin","visit","weight")
msw14ncit<-rbind(msw14ncit1,msw14ncit2)
msw14ncit[,1]<-as.factor(msw14ncit[,1])
msw14ncit[,2]<-as.factor(msw14ncit[,2])
msw14ncit[,3]<-as.numeric(msw14ncit[,3])

library(googleVis)
#plot(gvisSankey(msw13cit,from="origin",to="visit",weight="weight",options=list(height=700,width=1500,sankey="{link:{color:{fill:'deepskyblue'}},node:{width:20,label:{fontSize:12,bold:true}}}")))

#plot(gvisSankey(msw13ncit,from="origin",to="visit",weight="weight",options=list(height=700,width=1500,sankey="{link:{color:{fill:'mediumspringgreen'}},node:{width:20,label:{fontSize:12,bold:true}}}")))

plot(gvisSankey(msw14cit,from="origin",to="visit",weight="weight",options=list(height=700,width=1500,sankey="{link:{color:{fill:'deepskyblue'}},node:{width:20,label:{fontSize:12,bold:true}}}")))

plot(gvisSankey(msw14ncit,from="origin",to="visit",weight="weight",options=list(height=700,width=1500,sankey="{link:{color:{fill:'mediumspringgreen'}},node:{width:20,label:{fontSize:12,bold:true}}}")))
```

Now, I will do circlized graph for majors in stem vs occupation and majors in non-stem vs occupation.
```{r}
pus14citstem<-pus14cit[pus14cit$STEM==1,]
pus14citnstem<-pus14cit[pus14cit$STEM==0,]
pus14ncitstem<-pus14ncit[pus14ncit$STEM==1,]
pus14ncitnstem<-pus14ncit[pus14ncit$STEM==0,]

# each top major
pus14citstemtop<-list()
for(i in 1:10){
  pus14citstemtop[[i]]<-pus14citstem%>%filter(FOD1P==as.numeric(ms14cittops$major[i]))
}
pus14citnstemtop<-list()
for(i in 1:10){
  pus14citnstemtop[[i]]<-pus14citnstem%>%filter(FOD1P==as.numeric(ms14cittopns$major[i]))
}
pus14ncitstemtop<-list()
for(i in 1:10){
  pus14ncitstemtop[[i]]<-pus14ncitstem%>%filter(FOD1P==as.numeric(ms14ncittops$major[i]))
}
pus14ncitnstemtop<-list()
for(i in 1:10){
  pus14ncitnstemtop[[i]]<-pus14ncitnstem%>%filter(FOD1P==as.numeric(ms14ncittopns$major[i]))
}

# amount of jobs in each field for each top major
citstemf14<-list()
for(i in 1:10){
  citstemf14[[i]]<-as.data.frame(sort(table(pus14citstemtop[[i]]$OCCP.TYPE),decreasing=T))
}
citnstemf14<-list()
for(i in 1:10){
  citnstemf14[[i]]<-as.data.frame(sort(table(pus14citnstemtop[[i]]$OCCP.TYPE),decreasing=T))
}
ncitstemf14<-list()
for(i in 1:10){
  ncitstemf14[[i]]<-as.data.frame(sort(table(pus14ncitstemtop[[i]]$OCCP.TYPE),decreasing=T))
}
ncitnstemf14<-list()
for(i in 1:10){
  ncitnstemf14[[i]]<-as.data.frame(sort(table(pus14ncitnstemtop[[i]]$OCCP.TYPE),decreasing=T))
}

for(i in 1:10){
  citstemf14[[i]]<-citstemf14[[i]]%>%mutate(type=rownames(citstemf14[[i]]))
  citnstemf14[[i]]<-citnstemf14[[i]]%>%mutate(type=rownames(citnstemf14[[i]]))
  ncitstemf14[[i]]<-ncitstemf14[[i]]%>%mutate(type=rownames(ncitstemf14[[i]]))
  ncitnstemf14[[i]]<-ncitnstemf14[[i]]%>%mutate(type=rownames(ncitnstemf14[[i]]))
  colnames(citstemf14[[i]])[1]<-"frequency"
  colnames(citnstemf14[[i]])[1]<-"frequency"
  colnames(ncitstemf14[[i]])[1]<-"frequency"
  colnames(ncitnstemf14[[i]])[1]<-"frequency"
}
for(i in 1:10){
  citstemf14[[i]]<-citstemf14[[i]][order(citstemf14[[i]]$type),]
  citnstemf14[[i]]<-citnstemf14[[i]][order(citnstemf14[[i]]$type),]
  ncitstemf14[[i]]<-ncitstemf14[[i]][order(ncitstemf14[[i]]$type),]
  ncitnstemf14[[i]]<-ncitnstemf14[[i]][order(ncitnstemf14[[i]]$type),]
}

citstemm14<-matrix(0,nrow=10,ncol=25)
citnstemm14<-matrix(0,nrow=10,ncol=25)
ncitstemm14<-matrix(0,nrow=10,ncol=25)
ncitnstemm14<-matrix(0,nrow=10,ncol=25)
for(i in 1:10){
  citstemm14[i,]<-citstemf14[[i]]$frequency[2:26]
  citnstemm14[i,]<-citnstemf14[[i]]$frequency[2:26]
  ncitstemm14[i,]<-ncitstemf14[[i]]$frequency[2:26]
  ncitnstemm14[i,]<-ncitnstemf14[[i]]$frequency[2:26]
}
colnames(citstemm14)<-citstemf14[[1]]$type[2:26]
colnames(citnstemm14)<-citnstemf14[[1]]$type[2:26]
colnames(ncitstemm14)<-ncitstemf14[[1]]$type[2:26]
colnames(ncitnstemm14)<-ncitnstemf14[[1]]$type[2:26]
rownames(citstemm14)<-c(1,2,3,4,5,6,7,8,9,10)
rownames(citnstemm14)<-c(1,2,3,4,5,6,7,8,9,10)
rownames(ncitstemm14)<-c(1,2,3,4,5,6,7,8,9,10)
rownames(ncitnstemm14)<-c(1,2,3,4,5,6,7,8,9,10)
for(i in 1:10){
  rownames(citstemm14)[i]<-codename(ms14cittops$major[i])
  rownames(citnstemm14)[i]<-codename(ms14cittopns$major[i])
  rownames(ncitstemm14)[i]<-codename(ms14ncittops$major[i])
  rownames(ncitnstemm14)[i]<-codename(ms14ncittopns$major[i])
}
```

Visualization
```{r}
library(recharts)
zero1010<-matrix(0,10,10)
zero2525<-matrix(0,25,25)
citstemm14c1<-cbind(zero1010,citstemm14)
citstemm14c2<-cbind(t(citstemm14),zero2525)
citstemm14c<-rbind(citstemm14c1,citstemm14c2)
chordcitstem=list(title=list(text='Citizen STEM',subtext='From JavaScript',x='right',y='bottom'),
tooltip=list(trigger='item',formatter=JS('function(params){
                      if (params.indicator2) { // is edge
                        return params.value.weight;
                      } else {// is node
                        return params.name
                      }
                                                           }')),
toolbox=list(show=TRUE,feature=list(restore=list(show=TRUE),magicType=list(show=TRUE,type=c('force','chord')),
saveAsImage=list(show=TRUE))),
legend=list(x='left',data=c(rownames(citstemm14),colnames(citstemm14))),
series=list(list(type='chord',showScale=FALSE,showScaleText=FALSE,
data=list(list(name=rownames(citstemm14)[1]),list(name=rownames(citstemm14)[2]),list(name=rownames(citstemm14)[3]),list(name=rownames(citstemm14)[4]),list(name=rownames(citstemm14)[5]),list(name=rownames(citstemm14)[6]),list(name=rownames(citstemm14)[7]),list(name=rownames(citstemm14)[8]),list(name=rownames(citstemm14)[9]),list(name=rownames(citstemm14)[10]),list(name=colnames(citstemm14)[1]),list(name=colnames(citstemm14)[2]),list(name=colnames(citstemm14)[3]),list(name=colnames(citstemm14)[4]),list(name=colnames(citstemm14)[5]),list(name=colnames(citstemm14)[6]),list(name=colnames(citstemm14)[7]),list(name=colnames(citstemm14)[8]),list(name=colnames(citstemm14)[9]),list(name=colnames(citstemm14)[10]),list(name=colnames(citstemm14)[11]),list(name=colnames(citstemm14)[12]),list(name=colnames(citstemm14)[13]),list(name=colnames(citstemm14)[14]),list(name=colnames(citstemm14)[15]),list(name=colnames(citstemm14)[16]),list(name=colnames(citstemm14)[17]),list(name=colnames(citstemm14)[18]),list(name=colnames(citstemm14)[19]),list(name=colnames(citstemm14)[20]),list(name=colnames(citstemm14)[21]),list(name=colnames(citstemm14)[22]),list(name=colnames(citstemm14)[23]),list(name=colnames(citstemm14)[24]),list(name=colnames(citstemm14)[25])),
itemStyle=list(normal=list(label=list(show=TRUE))),
matrix=citstemm14c)))
echart(chordcitstem)
```

```{r}
zero1010<-matrix(0,10,10)
zero2525<-matrix(0,25,25)
citnstemm14c1<-cbind(zero1010,citnstemm14)
citnstemm14c2<-cbind(t(citnstemm14),zero2525)
citnstemm14c<-rbind(citnstemm14c1,citnstemm14c2)
chordcitnstem=list(title=list(text='Citizen non-STEM',subtext='From JavaScript',x='right',y='bottom'),
tooltip=list(trigger='item',formatter=JS('function(params){
                      if (params.indicator2) { // is edge
                        return params.value.weight;
                      } else {// is node
                        return params.name
                      }
                                                           }')),
toolbox=list(show=TRUE,feature=list(restore=list(show=TRUE),magicType=list(show=TRUE,type=c('force','chord')),
saveAsImage=list(show=TRUE))),
legend=list(x='left',data=c(rownames(citnstemm14),colnames(citnstemm14))),
series=list(list(type='chord',showScale=FALSE,showScaleText=FALSE,
data=list(list(name=rownames(citnstemm14)[1]),list(name=rownames(citnstemm14)[2]),list(name=rownames(citnstemm14)[3]),list(name=rownames(citnstemm14)[4]),list(name=rownames(citnstemm14)[5]),list(name=rownames(citnstemm14)[6]),list(name=rownames(citnstemm14)[7]),list(name=rownames(citnstemm14)[8]),list(name=rownames(citnstemm14)[9]),list(name=rownames(citnstemm14)[10]),list(name=colnames(citnstemm14)[1]),list(name=colnames(citnstemm14)[2]),list(name=colnames(citnstemm14)[3]),list(name=colnames(citnstemm14)[4]),list(name=colnames(citnstemm14)[5]),list(name=colnames(citnstemm14)[6]),list(name=colnames(citnstemm14)[7]),list(name=colnames(citnstemm14)[8]),list(name=colnames(citnstemm14)[9]),list(name=colnames(citnstemm14)[10]),list(name=colnames(citnstemm14)[11]),list(name=colnames(citnstemm14)[12]),list(name=colnames(citnstemm14)[13]),list(name=colnames(citnstemm14)[14]),list(name=colnames(citnstemm14)[15]),list(name=colnames(citnstemm14)[16]),list(name=colnames(citnstemm14)[17]),list(name=colnames(citnstemm14)[18]),list(name=colnames(citnstemm14)[19]),list(name=colnames(citnstemm14)[20]),list(name=colnames(citnstemm14)[21]),list(name=colnames(citnstemm14)[22]),list(name=colnames(citnstemm14)[23]),list(name=colnames(citnstemm14)[24]),list(name=colnames(citnstemm14)[25])),
itemStyle=list(normal=list(label=list(show=TRUE))),
matrix=citnstemm14c)))
echart(chordcitnstem)
```

```{r}
zero1010<-matrix(0,10,10)
zero2525<-matrix(0,25,25)
ncitstemm14c1<-cbind(zero1010,ncitstemm14)
ncitstemm14c2<-cbind(t(ncitstemm14),zero2525)
ncitstemm14c<-rbind(ncitstemm14c1,ncitstemm14c2)
chordncitstem=list(title=list(text='non-Citizen STEM',subtext='From JavaScript',x='right',y='bottom'),
tooltip=list(trigger='item',formatter=JS('function(params){
                      if (params.indicator2) { // is edge
                        return params.value.weight;
                      } else {// is node
                        return params.name
                      }
                                                           }')),
toolbox=list(show=TRUE,feature=list(restore=list(show=TRUE),magicType=list(show=TRUE,type=c('force','chord')),
saveAsImage=list(show=TRUE))),
legend=list(x='left',data=c(rownames(ncitstemm14),colnames(ncitstemm14))),
series=list(list(type='chord',showScale=FALSE,showScaleText=FALSE,
data=list(list(name=rownames(ncitstemm14)[1]),list(name=rownames(ncitstemm14)[2]),list(name=rownames(ncitstemm14)[3]),list(name=rownames(ncitstemm14)[4]),list(name=rownames(ncitstemm14)[5]),list(name=rownames(ncitstemm14)[6]),list(name=rownames(ncitstemm14)[7]),list(name=rownames(ncitstemm14)[8]),list(name=rownames(ncitstemm14)[9]),list(name=rownames(ncitstemm14)[10]),list(name=colnames(ncitstemm14)[1]),list(name=colnames(ncitstemm14)[2]),list(name=colnames(ncitstemm14)[3]),list(name=colnames(ncitstemm14)[4]),list(name=colnames(ncitstemm14)[5]),list(name=colnames(ncitstemm14)[6]),list(name=colnames(ncitstemm14)[7]),list(name=colnames(ncitstemm14)[8]),list(name=colnames(ncitstemm14)[9]),list(name=colnames(ncitstemm14)[10]),list(name=colnames(ncitstemm14)[11]),list(name=colnames(ncitstemm14)[12]),list(name=colnames(ncitstemm14)[13]),list(name=colnames(ncitstemm14)[14]),list(name=colnames(ncitstemm14)[15]),list(name=colnames(ncitstemm14)[16]),list(name=colnames(ncitstemm14)[17]),list(name=colnames(ncitstemm14)[18]),list(name=colnames(ncitstemm14)[19]),list(name=colnames(ncitstemm14)[20]),list(name=colnames(ncitstemm14)[21]),list(name=colnames(ncitstemm14)[22]),list(name=colnames(ncitstemm14)[23]),list(name=colnames(ncitstemm14)[24]),list(name=colnames(ncitstemm14)[25])),
itemStyle=list(normal=list(label=list(show=TRUE))),
matrix=ncitstemm14c)))
echart(chordncitstem)
```

```{r}
zero1010<-matrix(0,10,10)
zero2525<-matrix(0,25,25)
ncitnstemm14c1<-cbind(zero1010,ncitnstemm14)
ncitnstemm14c2<-cbind(t(ncitnstemm14),zero2525)
ncitnstemm14c<-rbind(ncitnstemm14c1,ncitnstemm14c2)
chordncitnstem=list(title=list(text='non-Citizen non-STEM',subtext='From JavaScript',x='right',y='bottom'),
tooltip=list(trigger='item',formatter=JS('function(params){
                      if (params.indicator2) { // is edge
                        return params.value.weight;
                      } else {// is node
                        return params.name
                      }
                                                           }')),
toolbox=list(show=TRUE,feature=list(restore=list(show=TRUE),magicType=list(show=TRUE,type=c('force','chord')),
saveAsImage=list(show=TRUE))),
legend=list(x='left',data=c(rownames(ncitnstemm14),colnames(ncitnstemm14))),
series=list(list(type='chord',showScale=FALSE,showScaleText=FALSE,
data=list(list(name=rownames(ncitnstemm14)[1]),list(name=rownames(ncitnstemm14)[2]),list(name=rownames(ncitnstemm14)[3]),list(name=rownames(ncitnstemm14)[4]),list(name=rownames(ncitnstemm14)[5]),list(name=rownames(ncitnstemm14)[6]),list(name=rownames(ncitnstemm14)[7]),list(name=rownames(ncitnstemm14)[8]),list(name=rownames(ncitnstemm14)[9]),list(name=rownames(ncitnstemm14)[10]),list(name=colnames(ncitnstemm14)[1]),list(name=colnames(ncitnstemm14)[2]),list(name=colnames(ncitnstemm14)[3]),list(name=colnames(ncitnstemm14)[4]),list(name=colnames(ncitnstemm14)[5]),list(name=colnames(ncitnstemm14)[6]),list(name=colnames(ncitnstemm14)[7]),list(name=colnames(ncitnstemm14)[8]),list(name=colnames(ncitnstemm14)[9]),list(name=colnames(ncitnstemm14)[10]),list(name=colnames(ncitnstemm14)[11]),list(name=colnames(ncitnstemm14)[12]),list(name=colnames(ncitnstemm14)[13]),list(name=colnames(ncitnstemm14)[14]),list(name=colnames(ncitnstemm14)[15]),list(name=colnames(ncitnstemm14)[16]),list(name=colnames(ncitnstemm14)[17]),list(name=colnames(ncitnstemm14)[18]),list(name=colnames(ncitnstemm14)[19]),list(name=colnames(ncitnstemm14)[20]),list(name=colnames(ncitnstemm14)[21]),list(name=colnames(ncitnstemm14)[22]),list(name=colnames(ncitnstemm14)[23]),list(name=colnames(ncitnstemm14)[24]),list(name=colnames(ncitnstemm14)[25])),
itemStyle=list(normal=list(label=list(show=TRUE))),
matrix=ncitnstemm14c)))
echart(chordncitnstem)
```

Now, I am going to check the employment rates. First, I will eliminate the rows with age greater than or equal to 66.
```{r}
pus11citstemy<-pus11cit[pus11cit$STEM==1&pus11cit$AGEP<66,]
pus11citnstemy<-pus11cit[pus11cit$STEM==0&pus11cit$AGEP<66,]
pus11ncitstemy<-pus11ncit[pus11ncit$STEM==1&pus11ncit$AGEP<66,]
pus11ncitnstemy<-pus11ncit[pus11ncit$STEM==0&pus11ncit$AGEP<66,]
pus12citstemy<-pus12cit[pus12cit$STEM==1&pus12cit$AGEP<66,]
pus12citnstemy<-pus12cit[pus12cit$STEM==0&pus12cit$AGEP<66,]
pus12ncitstemy<-pus12ncit[pus12ncit$STEM==1&pus12ncit$AGEP<66,]
pus12ncitnstemy<-pus12ncit[pus12ncit$STEM==0&pus12ncit$AGEP<66,]
pus13citstemy<-pus13cit[pus13cit$STEM==1&pus13cit$AGEP<66,]
pus13citnstemy<-pus13cit[pus13cit$STEM==0&pus13cit$AGEP<66,]
pus13ncitstemy<-pus13ncit[pus13ncit$STEM==1&pus13ncit$AGEP<66,]
pus13ncitnstemy<-pus13ncit[pus13ncit$STEM==0&pus13ncit$AGEP<66,]
pus14citstemy<-pus14cit[pus14cit$STEM==1&pus14cit$AGEP<66,]
pus14citnstemy<-pus14cit[pus14cit$STEM==0&pus14cit$AGEP<66,]
pus14ncitstemy<-pus14ncit[pus14ncit$STEM==1&pus14ncit$AGEP<66,]
pus14ncitnstemy<-pus14ncit[pus14ncit$STEM==0&pus14ncit$AGEP<66,]
```

Then, I will calculate the employment rate.
```{r}
citstememp<-c(nrow(pus11citstemy[!is.na(pus11citstemy$OCCP),])/nrow(pus11citstemy),nrow(pus12citstemy[!is.na(pus12citstemy$OCCP),])/nrow(pus12citstemy),nrow(pus13citstemy[!is.na(pus13citstemy$OCCP),])/nrow(pus13citstemy),nrow(pus14citstemy[!is.na(pus14citstemy$OCCP),])/nrow(pus14citstemy))
citnstememp<-c(nrow(pus11citnstemy[!is.na(pus11citnstemy$OCCP),])/nrow(pus11citnstemy),nrow(pus12citnstemy[!is.na(pus12citnstemy$OCCP),])/nrow(pus12citnstemy),nrow(pus13citnstemy[!is.na(pus13citnstemy$OCCP),])/nrow(pus13citnstemy),nrow(pus14citnstemy[!is.na(pus14citnstemy$OCCP),])/nrow(pus14citnstemy))
ncitstememp<-c(nrow(pus11ncitstemy[!is.na(pus11ncitstemy$OCCP),])/nrow(pus11ncitstemy),nrow(pus12ncitstemy[!is.na(pus12ncitstemy$OCCP),])/nrow(pus12ncitstemy),nrow(pus13ncitstemy[!is.na(pus13ncitstemy$OCCP),])/nrow(pus13ncitstemy),nrow(pus14ncitstemy[!is.na(pus14ncitstemy$OCCP),])/nrow(pus14ncitstemy))
ncitnstememp<-c(nrow(pus11ncitnstemy[!is.na(pus11ncitnstemy$OCCP),])/nrow(pus11ncitnstemy),nrow(pus12ncitnstemy[!is.na(pus12ncitnstemy$OCCP),])/nrow(pus12ncitnstemy),nrow(pus13ncitnstemy[!is.na(pus13ncitnstemy$OCCP),])/nrow(pus13ncitnstemy),nrow(pus14ncitnstemy[!is.na(pus14ncitnstemy$OCCP),])/nrow(pus14ncitnstemy))

```

Visualization
```{r}
empmat<-rbind(citstememp,citnstememp,ncitstememp,ncitnstememp)
colnames(empmat)<-c("2011","2012","2013","2014")
rownames(empmat)<-c("citizen STEM","citizen non-STEM","non-citizen STEM","non-citizen non-STEM")
empdf<-data.frame(year=factor(rep(c("2011","2012","2013","2014"),each=4),levels=c("2011","2012","2013","2014")),status=factor(rep(c("citizen STEM","citizen non-STEM","non-citizen STEM","non-citizen non-STEM"),4)),rate=c(empmat[,1],empmat[,2],empmat[,3],empmat[,4]))
library(ggplot2)
ggplot(data=empdf,aes(x=year,y=rate,fill=status))+geom_bar(stat="identity",position=position_dodge())


```

Now, I am going to calculate employment rate for each degree.
```{r}
pus14citstemyb<-pus14citstemy[pus14citstemy$SCHL==21,]
pus14citstemym<-pus14citstemy[pus14citstemy$SCHL==22,]
pus14citstemyp<-pus14citstemy[pus14citstemy$SCHL==23,]
pus14citstemyd<-pus14citstemy[pus14citstemy$SCHL==24,]
pus14citnstemyb<-pus14citnstemy[pus14citnstemy$SCHL==21,]
pus14citnstemym<-pus14citnstemy[pus14citnstemy$SCHL==22,]
pus14citnstemyp<-pus14citnstemy[pus14citnstemy$SCHL==23,]
pus14citnstemyd<-pus14citnstemy[pus14citnstemy$SCHL==24,]
pus14ncitstemyb<-pus14ncitstemy[pus14ncitstemy$SCHL==21,]
pus14ncitstemym<-pus14ncitstemy[pus14ncitstemy$SCHL==22,]
pus14ncitstemyp<-pus14ncitstemy[pus14ncitstemy$SCHL==23,]
pus14ncitstemyd<-pus14ncitstemy[pus14ncitstemy$SCHL==24,]
pus14ncitnstemyb<-pus14ncitnstemy[pus14ncitnstemy$SCHL==21,]
pus14ncitnstemym<-pus14ncitnstemy[pus14ncitnstemy$SCHL==22,]
pus14ncitnstemyp<-pus14ncitnstemy[pus14ncitnstemy$SCHL==23,]
pus14ncitnstemyd<-pus14ncitnstemy[pus14ncitnstemy$SCHL==24,]

citstemdeg<-c(nrow(pus14citstemyb[!is.na(pus14citstemyb$OCCP),])/nrow(pus14citstemyb),nrow(pus14citstemym[!is.na(pus14citstemym$OCCP),])/nrow(pus14citstemym),nrow(pus14citstemyp[!is.na(pus14citstemyp$OCCP),])/nrow(pus14citstemyp),nrow(pus14citstemyd[!is.na(pus14citstemyd$OCCP),])/nrow(pus14citstemyd))
citnstemdeg<-c(nrow(pus14citnstemyb[!is.na(pus14citnstemyb$OCCP),])/nrow(pus14citnstemyb),nrow(pus14citnstemym[!is.na(pus14citnstemym$OCCP),])/nrow(pus14citnstemym),nrow(pus14citnstemyp[!is.na(pus14citnstemyp$OCCP),])/nrow(pus14citnstemyp),nrow(pus14citnstemyd[!is.na(pus14citnstemyd$OCCP),])/nrow(pus14citnstemyd))
ncitstemdeg<-c(nrow(pus14ncitstemyb[!is.na(pus14ncitstemyb$OCCP),])/nrow(pus14ncitstemyb),nrow(pus14ncitstemym[!is.na(pus14ncitstemym$OCCP),])/nrow(pus14ncitstemym),nrow(pus14ncitstemyp[!is.na(pus14ncitstemyp$OCCP),])/nrow(pus14ncitstemyp),nrow(pus14ncitstemyd[!is.na(pus14ncitstemyd$OCCP),])/nrow(pus14ncitstemyd))
ncitnstemdeg<-c(nrow(pus14ncitnstemyb[!is.na(pus14ncitnstemyb$OCCP),])/nrow(pus14ncitnstemyb),nrow(pus14ncitnstemym[!is.na(pus14ncitnstemym$OCCP),])/nrow(pus14ncitnstemym),nrow(pus14ncitnstemyp[!is.na(pus14ncitnstemyp$OCCP),])/nrow(pus14ncitnstemyp),nrow(pus14ncitnstemyd[!is.na(pus14ncitnstemyd$OCCP),])/nrow(pus14ncitnstemyd))

degmat<-rbind(citstemdeg,citnstemdeg,ncitstemdeg,ncitnstemdeg)
colnames(degmat)<-c("bachelor","master","professional","doctorate")
rownames(degmat)<-c("citizen STEM","citizen non-STEM","non-citizen STEM","non-citizen non-STEM")
degdf<-data.frame(degree=factor(rep(c("bachelor","master","professional","doctorate"),each=4),levels=c("bachelor","master","professional","doctorate")),status=factor(rep(c("citizen STEM","citizen non-STEM","non-citizen STEM","non-citizen non-STEM"),4)),rate=c(degmat[,1],degmat[,2],degmat[,3],degmat[,4]))
ggplot(data=degdf,aes(x=degree,y=rate,fill=status))+geom_bar(stat="identity",position=position_dodge())
```

